TODO

### 2021-03-22 publications/The_tool_intro/paper.tex
pub: add bib

	Considering related work there are many research applying specific analysis technics for P4. Most of them concentrate on error checking of P4 programs. For example Assert-P4 \cite{Assert-P4} and Vera \cite{Vera} ask annotated P4 source from the developer and with symbolic execution they check if the predefined properties are correct during the program, although Vera can also detect common errors without annotations. P4V \cite{P4V} creates a formula, which describe the proper behavior of the program and checks the satisfiability of it with SMT solver. These tools are created for an earlier version of P4, namely P4$_\text{14}$. There are also verification tools, which can manage the newer version (P4$_\text{16}$) too. BF4 \cite{bf4} is created as a p4c backend, which can not only detect error possibilities, but it is able to repair them by adding new keys to the table and modify the table contents. An other tool p4-data-flow \cite{p4dataflow} uses data flow analysis to detect potential bugs in P4 switch codes.
	Some other tools uses analysis methods for different pruposes. For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.

@@

  The approach of the checking is defined in our previous paper \cite{cscs2020}, but shortly, it calculates the pre-and post-condition of the different blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program and based on their results it can detect improper usage of the fields and headers. Three types of cases can be detected: when there are some error cases in a block; when there is any inconsistency between the blocks; and when the need of the parser-deparser is inconsistent with the need of the control function.

>>>>

	Considering related work there are many research applying specific analysis technics for P4. Most of them concentrate on error checking of P4 programs. For example Assert-P4 \cite{assertp4} and Vera \cite{vera} ask annotated P4 source from the developer and with symbolic execution they check if the predefined properties are correct during the program, although Vera can also detect common errors without annotations. P4V \cite{p4v} creates a formula, which describe the proper behavior of the program and checks the satisfiability of it with SMT solver. These tools are created for an earlier version of P4, namely P4$_\text{14}$. There are also verification tools, which can manage the newer version (P4$_\text{16}$) too. BF4 \cite{bf4} is created as a p4c backend, which can not only detect error possibilities, but it is able to repair them by adding new keys to the table and modify the table contents. An other tool p4-data-flow \cite{p4dataflow} uses data flow analysis to detect potential bugs in P4 switch codes.
	Some other tools uses analysis methods for different pruposes. For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.

@@

  The approach of the checking is defined in our previous paper \cite{ownCheck}, but shortly, it calculates the pre-and post-condition of the different blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program and based on their results it can detect improper usage of the fields and headers. Three types of cases can be detected: when there are some error cases in a block; when there is any inconsistency between the blocks; and when the need of the parser-deparser is inconsistent with the need of the control function.
